Detection and characterisation of stellar multiplicity with Gaia

### 2018-06-29 article/ms.tex
words

\documentclass[twocolumn]{aastex61}
\usepackage{bm}
\usepackage{color}

@@

There are many ways that binaries can be reliably identified using \Gaia\
data, including radial velocity measurements, photometry, and astrometry.
These detection methods are sensitive to binary systems with different 
properties. Here we describe the radial velocity information that forms 
part of our model before describing how photometry and astrometry are 
incorporated into the detection and characterisation of stellar multiples.

@@

Radial velocity measurements are not available for individual epochs in the 
second \Gaia\ data release \citep{Lindegren:2018,Cropper:2018}, but the a radial velocity point estimate and error
is available for 7,224,631 sources \cite{Cropper:2018}. 
The radial velocity error provided by \Gaia\ ($\GaiaRVE$; column name \texttt{radial\_velocity\_error}) 
is a function of the number of transits $N$ (i.e., the number of observations; 
represented by column \texttt{rv\_nb\_transits}) and the scatter among those $N$ measurements. 
This allows us to calculate the scatter among those measurements, which we will
refer to as the \emph{radial velocity jitter}, for each source
\begin{eqnarray}
\RVJitter = \sqrt{\frac{2N}{\pi}}\GaiaRVE \quad .
\end{eqnarray}

For a single star (without a significant mass companion) the source radial velocity
jitter represents the minimum uncertainty with which \Gaia\ can measure 
radial velocity for a star of that apparent brightness and colour. However for 
stars with stellar companions and no evidence of double lines or binarity in the
cross-correlation-function, so-called SB1 type systems \citep{someone}, the
radial velocity jitter is a function of the orbital parameters and observation
epochs. We assume that the distribution of radial velocity jitter in the second
\Gaia\ data release is a mixture of two populations:

\begin{enumerate}
\item \emph{single-star systems}, where the radial velocity jitter represents the
      minimum radial velocity noise that \Gaia\ can measure for a star of that
      apparent magnitude and colour; and

\item \emph{higher-order star systems}, where the radial velocity jitter is
      significantly above that for single-star systems of a similar apparent
      magnitude and colour.
\end{enumerate}

We make a number of other explicit assumptions about the radial velocity
measurements reported by \Gaia:

\begin{itemize}
	\item the radial velocity jitter is a function of the apparent brightness 
		  of the point source
	\item the radial velocity jitter is a function of the apparent $bp-rp$
		  colour of the point source
	\item there is some intrinsic spread to the radial velocity jitter of
		  single stars, and that intrinsic spread also increases with the 
		  apparent brightness and colour of the source
	\item the difference between the true surface gravity $\logg$ and the
		  surface gravity of the radial velocity template used
		  (column \texttt{rv\_template\_logg}) has no impact on the radial
		  velocity jitter
	\item the difference between the true stellar metallicity [Fe/H] and
	 	  the metallicity of the radial velocity template used
		  (column \texttt{rv\_template\_feh}) has no impact on the radial
		  velocity jitter
	\item \todo{state something about teff template}		  
\end{itemize}

Conditioned on these assumptions, we adopt a two-component mixture model for 
the radial velocity jitter: a normal distribution where the mean and variance
are a function of stellar properties, and a uniform background component to
account for stellar multiples. Specifically, the likelihood is

\begin{eqnarray}
%	\mathcal{L} & \equiv & p\left(\{y
    MODEL
\end{eqnarray}

\noindent{}where \todo{X is Y} abd .

@@

Many sources in the second \Gaia\ data release do not have any reported radial 
velocity measurement, despite being bright enough ($G \lesssim 13$) and in a
suitable temperature range (e.g., between $X$ and $Y$) for radial velocities to 
be measured \citep{someone}. The principle reason why radial velocity measurements 
are \emph{not} reported for these stars is because the \Gaia/DPAC team have 
identified the source to be a double-lined spectroscopic binary (a SB2-type system), 
either through a composition of two stellar sources present in the spectra, or
from multiple (significant) modes in the cross-correlation function. In these
situations it is not sensible to report a point estimate of the radial velocity
of the point source. For fainter or bluer sources, however, the radial velocity 
may not be reported simply because it is too faint, blue, or red.

We calculated the completeness of radial velocity measurements (e.g., the
fraction of sources with reported radial velocities) as a function of all 
available source properties that might affect whether the radial velocity may
be reported or not. This included position ($\alpha$, $\delta$, $l$, $b$),
parallax, proper motions, apparent magnitudes, colours, properties of the radial
velocity templates, stellar parameters ($\teff$, $\radius$, $\luminosity$),
and other properties. The full list of properties investigated is described in
Appendix \ref{appendix:sb2}. In Figure \ref{fig:radial_velocity_completeness} 
we show the completeness as a function of some pertinent properties, which demonstrate 
that the radial velocity completeness is relatively flat until a star becomes 
too faint (low \rp\ flux), or is either too blue or too red. We adopt 
conservative limits for when the radial velocity completeness starts to drop 
with these properties, and we assume that any source within the following
parameter range
\begin{eqnarray}
    \mathrm{phot\,\,rp\,\,mean\,\,flux} & \in & [10^{4}, 10^8] \nonumber \\
    \mathrm{bp-rp} & \in & [X, Y] 
    \label{eq:sb2_criteria}
\end{eqnarray}
\noindent{}is likely to be a double-lined spectroscopic binary (SB2) if no 
radial velocity is reported. That is to say that we are explicitly assuming
that if a point source meets the criteria in Equation \ref{eq:sb2_criteria} 
and does not have a radial velocity measurement, then the point source is
an unresolved double-lined spectroscopic binary. In principle we could
make more realistic attempts to model the radial velocity completeness as
a function of stellar properties rather than simply stating ``sources within
this parameter range should have radial velocities unless they are SB2 systems'',
but the radial velocity completeness within our specified range is reasonably
flat.

In Section \ref{sec:discussion} we detail some of the immediate limitations or 
interpretations of this assumption, but here we  note that the probability of a 
source being a double-lined spectroscopic binary is calculated (or rather, 
deduced) separately to our calculations of binarity probability given 
\emph{measured} quantities like radial velocity, astrometry, and photometric 
colours. And as we discuss in Section \ref{sec:discussion}, the main conclusions
of this work do not depend on SB2 systems. Nevertheless, we \emph{strongly} 
caution that our deductive inference of SB2 systems will be far more uncertain 
than the binary probabilities we derive from other information. Our indicator 
whether a star is likely a SB2 system likely suffers from more contamination
and lower completeness compared to the probabilities we derive from other information
(e.g., the radial velocity jitter, astrometric excess noise, and photometric 
colours), and the contamination and completeness likely vary over some
complex (unknown) function of parameter space.

% Figure: radial velocity fraction as a function of galactic latitude and
% 		  longitude

@@

\subsection{Astrometric binaries}

Many higher-order star systems are unresolved point sources in \Gaia, but the
stellar companion(s) have sufficient mass to measurably affect the tangential 
velocity of the primary and produce a jitter in astrometric positions. There are
many other sources of astrometric jitter, but here we show that the principle
effect of astrometric excess noise is due to stellar companions. Note that due
to the astrometry `degree of freedom bug' in the processing of the second \Gaia\
data release \citep[e.g., see Appendix A1 of ][]{Lindegren:2018}, we only make
use of astrometric excess noise from the \todo{Tycho-Gaia Astrometric Solution}
\citep{Michalik:2015, Lindegren:2016}.

\begin{itemize}
    \item when would we expect AEN? what stellar or orbital properties does it 
          correlate or grow with?
    \item calibration model for AEN in DR1
\end{itemize}

@@

\section{Discussion}

@@

% At least some of these people will be promoted to the author list.
It is a pleasure to thank
	Berry Holl (Geneva),
	Jose Hernandez (ESAC),
	Daniel Michalik (ESA/ESTEC),
	Kevin C. Schlaufman (Johns Hopkins University),
		and
	Lorenzo Spina (Monash University).
This work was supported in part by the Australian Research Council 
through Discovery Grant DP160100637.
This work has made use of data from the European Space Agency (ESA) mission {\it
Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data
Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.  This research was
developed in part at the NYC Gaia DR2 Workshop at the Center for Computational
Astrophysics of the Flatiron Institute in 2018 April.

>>>>

\documentclass[twocolumn]{aastex61}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{color}

@@

There are many ways that binaries can be reliably identified using \Gaia\
data, including radial velocity measurements, photometry, and astrometry.
These detection methods are sensitive to binary systems with different 
properties. Here we describe the absence of reported radial velocity in
\Gaia\ data can be used to deduce stellar multiples, before we describe
our model that incorporates measurements of radial velocity, astrometry, 
and photometry, to detect and characterise stellar multiples.

Many sources in the second \Gaia\ data release do not have a reported radial 
velocity, despite being bright enough ($G \lesssim 13$) and in a suitable 
temperature range (e.g., between $\approx4000\,\textrm{K}$ and $\approx6500\,\textrm{K}$) 
for radial velocities to be measured \citep{Cropper:2018}. The principle reason 
why radial velocity measurements are \emph{not} reported for these stars is 
because the \Gaia/DPAC team have identified the source to be a double-lined 
spectroscopic binary (a so-called SB2-type system), either through a 
composition of two stellar sources present in the spectra, or from multiple 
(significant) modes in the cross-correlation function. In these situations it
is not sensible to report a point estimate of the radial velocity of the point 
source. For fainter or bluer sources, however, the radial velocity 
may not be reported simply because it is too faint, blue, or red.

We calculated the completeness of radial velocity measurements (e.g., the
fraction of sources with reported radial velocities) as a function of all 
available source properties that might affect whether the radial velocity may
be reported or not. This included position ($\alpha$, $\delta$, $l$, $b$),
parallax, proper motions, apparent magnitudes, \bp\ - \rp\ colour, 
properties of the radial velocity templates, stellar parameters ($\teff$, $\radius$, $\luminosity$),
and other properties. The full list of properties investigated is described in
Appendix \ref{appendix:sb2}, with corresponding figures.

In Figure \ref{fig:radial_velocity_completeness} we show the completeness as 
a function of some pertinent properties, which demonstrate that the radial 
velocity completeness is relatively flat until a source becomes too faint 
(low \rp\ flux), or is either too blue or too red. We adopt conservative 
limits for when the radial velocity completeness starts to drop with these 
properties, and we assume that any source within the following range of 
source parameters
\begin{eqnarray}
    \mathrm{phot\,\,rp\,\,mean\,\,flux} & \in & [10^{4}, 10^8] \nonumber \\
    \mathrm{bp-rp} & \in & [X, Y] 
    \label{eq:sb2_criteria}
\end{eqnarray}
\noindent{}is likely to be a double-lined spectroscopic binary (SB2) if no 
radial velocity is reported. That is to say that we are explicitly assuming
that if a point source meets the criteria in Equation \ref{eq:sb2_criteria} 
and does not have a reported radial velocity measurement, then the point 
source is an unresolved double-lined spectroscopic binary. In principle we 
could make more realistic attempts to model the radial velocity completeness as
a function of stellar properties rather than simply stating ``sources within
this parameter range should have radial velocities unless they are SB2 systems'',
but the radial velocity completeness within our specified range is reasonably
flat.

\todo{Some confirmation of this? The properties of SB2 candidate systems relative to others. Figure \ref{fig:sb2_histograms}.}

We stress that our sample of SB2 type systems is calculated (or rather, deduced)
separately to our calculations of multiplicity probability given the 
\emph{measured} quantities from \Gaia\ like radial velocity, astrometry, and
photometry. In Section \ref{sec:discussion} we detail some of the immediate
limitations or interpretations of this assumption, and we emphasise that the 
main conclusions of this work do not depend on SB2 systems. Nevertheless, we 
\emph{strongly} 
caution that our deductive inference of SB2 systems will be far more uncertain 
than the binary probabilities we derive from other information. Our indicator 
whether a star is likely a SB2 system likely suffers from more contamination
and lower completeness compared to the probabilities we derive from other information
(e.g., the radial velocity jitter, astrometric excess noise, and photometric 
colours), and the contamination and completeness likely vary over some
complex (unknown) function of parameter space.

\begin{figure*}
	\includegraphics[width=1.0\textwidth]{../figures/todo.png}
    \caption{Fraction of \Gaia\ sources with reported radial velocities
		     as a function of source properties. Within the adopted source
		     parameter ranges (gray; see Section \ref{sec:sb2_methods})
		     the radial velocity completeness is approximately flat.
		     We flag sources within this range that do not have reported 
		     radial velocities to be candidate SB2 systems.}
    \label{fig:radial_velocity_completeness}
\end{figure*}

\begin{figure*}
	\includegraphics[width=1.0\textwidth,height=3.0in]{../figures/todo.png}
    \caption{Distribution of 
    			(a) photometric \bp\ - \rp\ excess factor, 
				(b) astrometric unit weight error, 
					and 
				(c) photometric variability
			of candidate SB2 type systems relative to a control sample.}
    \label{fig:sb2_histograms}
\end{figure*}

% Figure: radial veloci

@@

Radial velocity measurements are not available for individual epochs in the 
second \Gaia\ data release \citep{Lindegren:2018,Cropper:2018}, but a point estimate
and error in radial velocity is available for 7,224,631 sources \cite{Cropper:2018}.
% TODO: That's the value from the paper, but I think the true value is lower. Check.
The reported radial velocity error ($\GaiaRVE$; column name \texttt{radial\_velocity\_error}) 
is a function of the number of transits $N$ (i.e., the number of observations; 
represented by column \texttt{rv\_nb\_transits}) and the standard deviation among 
those $N$ measurements of radial velocity. This allows us to calculate the standard
deviation in radial velocity for each source, independent of the number of measurements,
which we will refer to as the \emph{radial velocity jitter} $\RVJitter$,
\begin{eqnarray}
\RVJitter = \sqrt{\frac{2N}{\pi}}\GaiaRVE \quad .
\end{eqnarray}

For a single star (without a significant mass companion) the source radial velocity
jitter represents the minimum uncertainty with which \Gaia\ can measure 
radial velocity for a star of that colour, apparent brightness, and absolute brightness.
However for stars with stellar companions and no evidence of double lines or binarity in the
cross-correlation-function, so-called SB1 type systems \citep{someone}, the
radial velocity jitter is a function of the orbital parameters and observation
epochs. We assume that the distribution of radial velocity jitter in the second
\Gaia\ data release is a mixture of two populations:

\begin{enumerate}
\item \emph{single-star systems}, where the radial velocity jitter represents the
      minimum radial velocity noise that \Gaia\ can measure for a star of that
      \bp\ - \rp\ colour, apparent \rp\ magnitude, and absolute \rp\ magnitude;

\item \emph{higher-order star systems}, where the radial velocity jitter is
      significantly above that for single-star systems of a similar colour, 
      apparent magnitude, and absolute magnitude.
\end{enumerate}

The mean radial velocity jitter of a single star will vary depending on the 
\bp\ - \rp\ colour of the source and the apparent magnitude. Similarly, the mean
radial velocity jitter of stellar \emph{multiples} will depend on the source 
colour and its position in the Hertzsprung-Russell diagram. For these reasons,
we must consider the radial velocity jitter of a source in context with other
sources that have a similar \bp\ - \rp\ colour, a similar apparent \rp\ magnitude,
and a similar absolute \rp\ magnitude. In principle if we knew the underlying
distribution and properties of stellar multiples then we could model how different
binary (and higher order) systems would be observable across the Hertszprung-Russell
diagram.

We chose to adopt a non-parametric model for stellar multiplicity across the
Hertsprung-Russell diagram because we do not know the distribution of properties
of stellar multiples. Specifically, for each source we take the following steps:

\begin{enumerate}

	\item Select sources with similar \bp\ - \rp\ colours, a similar apparent \rp\
		  magnitude, and a similar absolute \rp\ magnitude.

	\item We fit a two-component mixture model to the distribution of radial
		  velocity jitter for the subset of similar sources selected in Step 1.

	\item Evaluate whether the source of interest is more consistent with being
		  drawn from the single star component (the normal distribution) or the
		  stellar multiple component (the log-normal distribution).

	\item For sources that are more consistent with being drawn from the stellar
		  multiple component, provide a partial characterisation of the system by
		  calculating the excess radial velocity jitter (above what is expected 
		  for a single star with similar observed properties), among other 
		  quantities.

\end{enumerate}

We illustrate this procedure in Figure \ref{fig:npm_schematic}, where we demonstrate
how the distribution of source properties (e.g., radial velocity jitter) varies across
the Hertsprung-Russell diagram. While this model is flexible enough to describe varying
properties of single stars and stellar multiples, there are a number of explicit 
assumptions that go into this model:

\todo{assumptions}

\begin{figure*}
	\includegraphics[width=1.0\textwidth]{../figures/todo.png}
    \caption{Illustration of the method we adopt for identifying and characterising
    		 stellar multiplicity across the Hertsprung-Russell diagram. For each
		 	 \Gaia\ source we select between 128 and 1024 sources that have
			 similar \bp\ - \rp\ colours, apparent \rp\ magnitudes, and absolute \rp\
			 magnitudes (Step 1). With these similar sources we fit a two-component
			 model to distinguish single star sources from stellar multiples (Step 2).
			 With the model parameters optimised from Step 2, we evaluate probability
			 of stellar multiplicity and partially characterise the higher order
			 systems by assuming binarity and estimating the system semi-amplitude (Step 3).}
    \label{fig:npm_schematic}
\end{figure*}

\subsubsection*{Step 1: Selecting similar sources}

We construct a $k$-dimensional tree \citep[k-d tree;][]{} for all sources in the
dimensions of \bp\ - \rp\ colour, apparent \rp\ magnitude, and absolute \rp\ magnitude.
When doing so we scale the dimensions such that 0.1\,mags in \bp\ - \rp\ colour is
approximately equal to 1 magnitude in apparent \rp\ magnitude and 1 magnitude in 
absolute \rp\ magnitude. We use this k-d tree for constructing the `ball' of similar
stars for every source.

We enforce a number of constraints when querying for similar stars. For each source
we require the `ball' in multi-dimensional space to include at least 128 sources.
We further require that the radius of the ball extends to at least 0.05\,mags in 
\bp\ - \rp\ colour, 0.5\,mags in apparent \rp\ magnitude, and 0.5\,mags in absolute
\rp\ magnitude. If the initial query of 128 points does not extend wide enough to
meet our constraints on minimum radius, we extend the radius (linearly in each scaled)
dimension until the minimum constraints on radii are met. Our minimum radii constraints
imply that there will be many (e.g., $>>128$) points returned in dense regions of the
Hertsprung-Russell diagram. In these situations we then subsample the selected points
to return a random 1024 sources in any ball, while enforcing our constraints on
minimum radii. As a result, the number of `similar' sources selected will range from
a minimum of 128 to a maximum of 1024, and the minimum radii constraints on various
dimensions are always maintained.

\subsubsection*{Step 2: Optimizing the two-component mixture}

We fit a two-component mixture model to the distribution of radial velocity jitter for
all similar sources selected through Step 1. This mixture model includes a normal
distribution to represent the intrinsic jitter for single stars, and a log-normal
distribution to represent stellar multiples. Specifically the model parameters include
a mixing weight parameter $\theta$ that is constrained between $(0, 1)$, the mean 
$\mu_{s}$ and standard deviation $\sigma_{s}$ of the normal distribution,
and the mean $\mu_{m}$ and standard deviation $\sigma_{m}$ of the 
log-normal distribution. For brevity we

We assume a beta prior on $\theta$  such that $\theta \sim \mathcal{B}\left(5, 5\right)$
and we require $\sigma_{s}$ and $\sigma_{m}$ to be larger than zero.
Depending on the distribution of the radial velocity jitter, we often found this mixture
challenging to optimize because the log-normal distribution could easily account for 
most of the observed distribution, which tended the mixing weight to zero and implied
that all selected sources were stellar multiples. To avoid this situation we placed a
constraint on the mean of the log-normal distribution to ensure that the \emph{mode}
of the log-normal distribution is between $\mu_{s} + 1\sigma_{s}$ and
$\mu_{s} + 5\sigma_{s}$. The mode of the log-normal distribution is
$\exp\left(\mu_{m} - \sigma_{m}^2\right)$ such that
\begin{eqnarray}
	\mu_{s} + 5\sigma_{s} & > & \exp\left(\mu_{m} - \sigma_{m}^2\right) \label{eq:rvm_lower_bound} \\
	\mu_{s} + 1\sigma_{s} & < & \exp\left(\mu_{m} - \sigma_{m}^2\right) \label{eq:rvm_upper_bound} \quad .
\end{eqnarray}

However, we found that this constraint alone was insufficient. Often the mode would
be very close to the $\mu_{s} + 1\sigma_{s}$ lower bound, which implies that
the log-normal distribution is providing a considerable fraction of probability support
to sources with radial velocity jitter near the mean of the \emph{normal} distribution.
For this reason we chose to alter our lower bound constraint in that we also required
that at the mean of the normal distribution, the cumulative probability distribution
of the log-normal must be less than 10\% (let $q = 0.10$). The cumulative distribution 
function for the log-normal distribution is
\begin{eqnarray}
\textrm{CDF}(x|\mu_{m},\sigma_{m}) = \frac{1}{2} + \frac{1}{2}\textrm{erf}\left(\frac{\log{x} - \mu_{m}}{\sqrt{2}\sigma_{m}}\right) 
\end{eqnarray}

\noindent{}where \textrm{erf} is the standard error function. We use the approximation 
to the error function 
\begin{eqnarray}
	\textrm{erf}\left(x\right) \approx \tanh\left(\sqrt{\pi}\log{2}x\right)
\end{eqnarray}

\noindent{}and use the identity
\begin{eqnarray}
	\tanh^{-1}\left(x\right) = \frac{1}{2}\left[\log{\left(1 + x\right)} - \log{\left(1 - x\right)}\right]
\end{eqnarray}

\noindent{}to write our constraint on $\mu_{m}$ as
\begin{eqnarray}
	\mu_{m} & > & \log\mu_{s} + \frac{\sigma_{m}}{2\log{2}}\sqrt{\frac{2}{\pi}}\log{\left(\frac{1}{q} - 1\right)} \nonumber \\
	\mu_{m} & > & \log\mu_{s} + \frac{\sigma_{m}}{2\log{2}}\sqrt{\frac{2}{\pi}}\log{9} \label{eq:rvm_lower_bound2} \quad .
\end{eqnarray}

Incorporating the bounds from Equations \ref{eq:rvm_lower_bound}, \ref{eq:rvm_upper_bound},
and \ref{eq:rvm_lower_bound2} leads to the prior
\begin{eqnarray}
	\mu_{m} \sim \mathcal{U}\left(\alpha, \beta\right)
\end{eqnarray}

\noindent{}where:
\begin{eqnarray}
  \alpha & = & \max\left(\!
	\begin{aligned}
		\log{\left(\mu_{s} + 1\sigma_{s}\right)} + \sigma_{m}^2\\
		\log\mu_{s} + \frac{\sigma_{m}}{2\log{2}}\sqrt{\frac{2}{\pi}}\log{9}
	\end{aligned}\right) \\
  \beta & = & \log{\left(\mu_{s} + 5\sigma_{s}\right)} + \sigma_{m}^2 \quad .
\end{eqnarray}

We found these priors were sufficient to ensure numerical stability and efficiency.

Wherever possible we initialised the model parameters from nearby points (within the
ball selected by the k-d tree) where an optimised result already exists. This was primarily to minimise
computational cost; the initialisation did not have a noticeable impact on the
optimised result. We required the log probability and the gradient of the log
probability to reach machine precision before considering the optimisation
converged. After convergence, we queried to see if any points within the ball of
similar stars had not been optimized. If no result existed, we would next move to that
point. We refer to this process as \emph{swarm optimisation}, which we conducted in 
parallel, and illustrate in Figure \ref{fig:swarm_optimisation}.

\todo{To minimise computational cost we assigned the closest 8 stars with the result
from others}

\subsubsection*{Step 3: Evaluating probability and system properties}

\todo{selecting similar sources}

\todo{fitting the two-component model}

\todo{evaluating probability}

\todo{calculating source properties}

@@

ty fraction as a function of galactic latitude and
% 		  longitude

@@

\subsection{Astrometric binaries} \label{sec:method_astrometric_binaries}

Many higher-order star systems are unresolved point sources in \Gaia, but the
stellar companion(s) may have sufficient mass to measurably affect the tangential 
velocity of the primary and produce a detectable jitter in the astrometric 
positions. There are many other sources of astrometric jitter, but here we show 
that the principle effect of astrometric excess noise is due to stellar 
companions. Note that due to the astrometry `degree of freedom bug' in the 
processing of the second \Gaia\ data release \citep[e.g., see Appendix A1 of ][]{Lindegren:2018}, 
that resulted in 80\% of sources having zero astrometric excess noise,
we instead make use of the astrometric unit weight error $u$
\begin{eqnarray}
	u = \sqrt{\frac{\chi^2_{al}}{N_{obs,al} - 5}}
\end{eqnarray}
\noindent{}where $\chi^2_{al}$ is the astrometric $\chi^2$ value
in the along-scan direction (column \texttt{astrometric\_chi2\_al}) and 
$N_{obs,al}$ is the number of astrometric observations in the along-scan
direction (column \texttt{astrometric\_n\_obs\_al}). The values of this
quantity can be interpreted similarly to how the astrometric excess noise
would be interpreted (e.g., large values are less consistent with a
single star model), although like the radial velocity and astrometric
jitter, it must be considered in context with stars of similar colour,
apparent magnitude (and preferably, absolute magnitude).

\subsection{Photometric binaries} \label{sec:method_photometric_binaries}

@@

\section{Discussion} \label{sec:discussion}

@@

% At least some of these people will be promoted to the author list.
It is a pleasure to thank
	Berry Holl (Observatoire de Gen\'eve),
	Jose Hernandez (ESAC),
	Daniel Michalik (ESA/ESTEC),
	Kevin C. Schlaufman (Johns Hopkins University),
	Lorenzo Spina (Monash University),
		and
	Sergey Koposov (Carnegie Mellon University).
This work was supported in part by the Australian Research Council 
through Discovery Grant DP160100637.
This work has made use of data from the European Space Agency (ESA) mission {\it
Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data
Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.  This research was
developed in part at the NYC Gaia DR2 Workshop at the Center for Computational
Astrophysics of the Flatiron Institute in 2018 April.
